Time Series Length at Which Block Bootstrapping is Effective for Estimation of Variance

### 2022-09-22 Manuscript/manuscript.tex
9/22 Notes

Block bootstrapping is a widely used method in Statistics. The concept for block 
bootstrapping was developed independently by. It has been applied to a variety of 
different fields such 
as econometrics \citep{MacKinnon} and meteorology \citep{Varga}. It can be used for 
situations in which there is temporal dependence and the goal is estimation or hypothesis 
testing. It is useful for a variety of applicationsAssuming that the sample is infinitely 
large, the method will work perfectly. However, for a finite sample size, the method will 
not work as well as expected. It may be necessary (in order to plan an applied 
statistical 
procedure) to know at which sample size the method stops working at an acceptable level. 
The goal of this study is to find a threshold or range of sample sizes at block bootstrap 
is no longer an effective method for estimating variance.

\citet{Nevitt} find that a sample size of 200-1000 is usually sufficient for standard 
bootstrap estimation. However, block bootstrapping is a different situation especially in 
the context of time series because the sample is split into blocks and there is a time 
dependence factor.

@@

In this experiment, there are certain factors that are expected to affect the coverage
rates. As the Auto-Regressive (AR) coefficient (the time dependence) of the time series 
increases,
we expect the coverage rates of the confidence intervals to decrease.
The coverage rates are also affected by the size of the blocks - more specifically,
how the size of the blocks (l) relates to the size of the time series (n) - 
and whether or not they overlap. It is known that as the size of the time series 
increases, the optimal block length should increase, and the ratio of the block length to 
the time series length should decrease. l = (n)(1/3) is typically considered the optimal 
block length according to asymptotic theory. If only perfect cubes are used for the time 
series length, n gets too large when l increases by relatively little. An alternative 
would be to use smaller time series, find the cube root, and set the block length to the 
nearest whole number. However, in this study l = sqrt{n} is used, as it allows for smaller 
sample sizes, but it still follows the aforementioned principle.

>>>>

Block bootstrapping is a widely used method in Statistics. The concept for block 
bootstrapping was developed independently by \citet{Hall}, \citet{Carlstein}, and 
\citet{Kunsch}. \citet{Radovanov} It has been applied to a variety of 
different fields such 
as econometrics \citep{MacKinnon} and meteorology \citep{Varga}. It can be used for 
situations in which there is temporal dependence and the goal is estimation or hypothesis 
testing. It is useful for a variety of applicationsAssuming that the sample is infinitely 
large, the method will work perfectly. However, for a finite sample size, the method will 
not work as well as expected. It may be necessary (in order to plan an applied 
statistical 
procedure) to know at which sample size the method stops working at an acceptable level. 
The goal of this study is to find a threshold or range of sample sizes at block bootstrap 
is no longer an effective method for estimating variance.

\citet{Nevitt} find that a sample size of 200-1000 is usually sufficient for standard 
bootstrap estimation. However, block bootstrapping is a different situation because the 
sample is split into blocks.

\citet{Goncalves} found that standard error estimates from block bootstrapping small 
samples 
may be significantly more accurate than inference from closed-form asymptotic estimates. 
This however, works only under the assumption of low dependence and heterogeneity. In the
context of a time series, it becomes more complicated.

@@

In this experiment, there are certain factors that are expected to affect the coverage
rates. As the Auto-Regressive (AR) coefficient (the time dependence) of the time series 
increases,
we expect the coverage rates of the confidence intervals to decrease.
The coverage rates are also affected by the size of the blocks - more specifically,
how the size of the blocks (l) relates to the size of the time series (n) - 
and whether or not they overlap. It is known that as the size of the time series 
increases, the optimal block length should increase, and the ratio of the block length to 
the time series length should decrease. l = n$^3$ is typically considered the optimal 
block length according to asymptotic theory. \citep{Buhlmann} If only perfect cubes are used for the time 
series length, n gets too large when l increases by relatively little. An alternative 
would be to use smaller time series, find the cube root, and set the block length to the 
nearest whole number. However, in this study l = sqrt{n} is used, as it allows for smaller 
sample sizes, but it still follows the aforementioned principle.
